---
title: "Personality preliminary data checking"
output: html_notebook
date: "11 Sept 2017"
---

```{r}
require(tidyverse)

load("pers.Rdata")
```

Remove my preview tests (n=5)

```{r}
pers <- filter(pers, distributionchannel != "preview")
```

Starting with n  = 660 participants
Check for and remove non-consenting participants. Initial consent (Q4/consent) 1 = Yes, 2 = Full info sheet 3 = No
Full info sheet (Q19) 1 = Yes, 2 = No

```{r}
table(pers$consent, useNA="ifany") #647 yes, 5 no, 8 full info, 1 NA
table(pers$q19, useNA="ifany") #7 further yes

pers <- filter(pers, consent==1|q19==1)
```

Now n=654

Looking at completion through to the end of the standardised questionnaires (Q20_28)

```{r}
table(is.na(pers$q20_28))

pers <- filter(pers, q20_28>0)
```

89 not completed, leaving n = 565.

Check for extreme times

```{r}
ggplot(pers, aes(`duration (in seconds)`)) +
  geom_histogram() +
  scale_x_continuous(limits = c(0,1200))

#zoom in on the super short
ggplot(pers, aes(`duration (in seconds)`)) +
  geom_histogram() +
  scale_x_continuous(limits = c(0,250))
```


Shortest finisher still took over a minute, so while fast, probably OK.

#save file for psychometrics
```{r}
save(pers, file="pers2.Rdata")
```

