---
title: "Psychometrics"
output:
  word_document: default
  html_notebook: default
date: "12 Sept 2017"
---

```{r}
require(tidyverse)
require(lavaan)
require(userfriendlyscience)
require(psych)

load("pers2.Rdata")

#reverse AGQ-R questions so that higher numbers indicate stronger agreement
pers <- mutate_at(pers, vars(q5_1:q5_12), ~6-.)

#reverse BFI questions so that higher numbers indicate stronger agreement (then reverse code several)
pers <- mutate_at(pers, vars(q22_45:q22_59), ~15-.) %>%
  mutate(q22_47 = 8-q22_47, q22_50 = 8-q22_50, q22_54 = 8-q22_54, q22_58 = 8-q22_58)

#reverse REI questions so that higher numbers indicate stronger agreement (except for first two items 19 & 20 which are reversed)
pers <- mutate_at(pers, vars(q20_21:q20_28), ~6-.) %>%
  mutate(q20_23 = 6 - q20_23)

#reverse CRO questions so that higher numbers indicate stronger agreement
pers <- mutate_at(pers, vars(q36_1:q36_8), ~8-.) 

#reverse pharmacist attitude variables so that higher numbers are pro pharmacist role
pers <- mutate_at(pers, vars(q37_1:q37_10), ~4-.)

#calculate new variables
# pers <- mutate(pers, mastery_approach = (q5_1 + q5_3 + q5_7) / 3, mastery_avoidance = (q5_5 + q5_9 + q5_11) / 3, 
#                performance_approach = (q5_2 + q5_4 + q5_8) / 3, performance_avoidance = (q5_6 + q5_10 + q5_12) / 3,
#                neuroticism = (q22_45 + q22_46 + q22_47) /3, extraversion = (q22_48 + q22_49 + q22_50)/3,
#                openness = (q22_51 + q22_52 + q22_53)/3, agreeableness = (q22_54 + q22_55 + q22_56)/3,
#                conscientiousness= (q22_57 + q22_58 + q22_59)/3,
#                need_for_cognition = (q20_19 + q20_20 + q20_21 + q20_22 + q20_23)/5,
#                faith_in_intuition = (q20_24 + q20_25 + q20_26 + q20_27 + q20_28)/5,
#                time_pressures = (q36_2 + q36_3)/2, reliance_on_dr = (q36_1 + q36_8)/2,
#                pharmacist_restriction = (q36_6 + q36_7)/2, side_effects = (q36_4 + q36_5)/2,
#                trad_role = (q37_1 + q37_2 + q37_3 + q37_4 + q37_5)/5,
#                new_role = (q37_7 + q37_8 + q37_9 + q37_10)/4)

#calculate new variables as POMP scoes
pers <- mutate(pers, mastery_approach = ((q5_1 + q5_3 + q5_7) / 3 - 1 ) / 4 * 100, 
               mastery_avoidance = ((q5_5 + q5_9 + q5_11) / 3 - 1 ) / 4 * 100, 
               performance_approach = ((q5_2 + q5_4 + q5_8) / 3 - 1 ) / 4 * 100, 
               performance_avoidance = ((q5_6 + q5_10 + q5_12) / 3 - 1 ) / 4 * 100,
               neuroticism = ((q22_45 + q22_46 + q22_47) /3 - 1 ) / 6 * 100, 
               extraversion = ((q22_48 + q22_49 + q22_50)/3 - 1 ) / 6 * 100,
               openness = ((q22_51 + q22_52 + q22_53)/3 - 1 ) / 6 *100, 
               agreeableness = ((q22_54 + q22_55 + q22_56)/3 - 1 ) / 6 * 100,
               conscientiousness= ((q22_57 + q22_58 + q22_59)/3 - 1 ) / 6 * 100,
               need_for_cognition = ((q20_19 + q20_20 + q20_21 + q20_22 + q20_23)/5 - 1) / 4 * 100,
               faith_in_intuition = ((q20_24 + q20_25 + q20_26 + q20_27 + q20_28)/5 - 1) / 4 * 100,
               time_pressures = ((q36_2 + q36_3)/2 - 1 ) / 6 * 100, 
               reliance_on_dr = ((q36_1 + q36_8)/2 - 1 ) / 6 * 100,
               pharmacist_restriction = ((q36_6 + q36_7)/2 - 1 ) / 6 * 100, 
               side_effects = ((q36_4 + q36_5)/2 - 1 ) / 6 * 100,
               trad_role = ((q37_1 + q37_2 + q37_3 + q37_4 + q37_5)/5 - 1) / 2 *100,
               new_role = ((q37_7 + q37_8 + q37_9 + q37_10)/4 - 1) / 2 *100)
               
save(pers, file = "pers3.Rdata")               

# p2.data <- select(pers, -id, -q38, -q20)
# save(p2.data, file = "dhanya_p2.Rdata")
# write.csv(p2.data, file = "dhanya_p2.csv")
```

#Achievement Goals Questionnaire Revised

Fit seems good, RMSEA ~.059
Omega reliabilities are acceptable (>.74)


```{r}
agr.model1 <- '
# latent variable definitions
mastery_approach =~ q5_1 + q5_3 + q5_7
mastery_avoidance =~ q5_5 + q5_9 + q5_11
performance_approach =~ q5_2 + q5_4 + q5_8
performance_avoidance =~ q5_6 + q5_10 + q5_12
'
agr.fit1 <- cfa(agr.model1, data=pers)
summary(agr.fit1, fit.measures = TRUE, standardized = TRUE)
 # standardizedSolution(agr.fit1)
 
select(pers, q5_1, q5_3, q5_7) %>%
  omega(nfactors = 1) #.74

select(pers, q5_5, q5_9, q5_11) %>%
  omega(nfactors = 1) #.74

select(pers, q5_2, q5_4, q5_8) %>%
  omega(nfactors = 1) #.84

select(pers, q5_6, q5_10, q5_12) %>%
  omega(nfactors = 1) #.87

save(pers, file = "pers3.Rdata")
```

#Big Five

Fit not great, but OK, RMSEA ~.082
Reverse scored items generally weaker loadings
Omega reliabilities are acceptable (>.60). Generally better than reported in the source paper (Lang et al., 2011)


```{r}
bfi.model1 <- '
# latent variable definitions
neuroticism =~ q22_45 + q22_46 + q22_47
extraversion =~ q22_48 + q22_49 + q22_50
openness =~ q22_51 + q22_52 + q22_53
agreeableness =~ q22_54 + q22_55 + q22_56
conscientiousness=~ q22_57 + q22_58 + q22_59
'
bfi.fit1 <- cfa(bfi.model1, data=pers)
summary(bfi.fit1, fit.measures = TRUE, standardized = TRUE)
 # standardizedSolution(bfi.fit1)
 
select(pers, q22_45, q22_46, q22_47) %>%
  omega(nfactors = 1) #.76

select(pers, q22_48, q22_49, q22_50) %>%
  omega(nfactors = 1) #.79

select(pers, q22_51, q22_52, q22_53) %>%
  omega(nfactors = 1) #.71

select(pers, q22_54, q22_55, q22_56) %>%
  omega(nfactors = 1) #.61

select(pers, q22_57, q22_58, q22_59) %>%
  omega(nfactors = 1) #.60
```

#Rational Experiential Inventory

Fit not great, but OK, RMSEA ~.076
Q23 weak loading on NFC, but fit worse without Q23
Omega reliabilities are good (>.80). 


```{r}
rei.model1 <- '
# latent variable definitions
need_for_cognition =~ q20_19 + q20_20 + q20_21 + q20_22 + q20_23
faith_in_intuition =~ q20_24 + q20_25 + q20_26 + q20_27 + q20_28
'
rei.fit1 <- cfa(rei.model1, data=pers)
summary(rei.fit1, fit.measures = TRUE, standardized = TRUE)
 # standardizedSolution(rei.fit1)
 
rei.model2 <- '
# latent variable definitions, with no Q23
need_for_cognition =~ q20_19 + q20_20 + q20_21 + q20_22 
faith_in_intuition =~ q20_24 + q20_25 + q20_26 + q20_27 + q20_28
'
rei.fit2 <- cfa(rei.model2, data=pers)
summary(rei.fit2, fit.measures = TRUE, standardized = TRUE)
 
select(pers, q20_19:q20_23) %>%
  omega(nfactors = 3, fm = "ml") #.78

select(pers, q20_19:q20_22) %>%
  omega(nfactors = 3, fm = "ml") #.79 DROPPING Q23 has little impact on reliability

select(pers, q20_24:q20_28) %>%
  omega(nfactors = 3, fm = "ml") #.82
```

#Counselor Role Orientation

Fit good, RMSEA ~.052; better without side-effect factor
But reliabilities low.


```{r}
cro.model1 <- '
# latent variable definitions
time pressures =~ q36_2 + q36_3
reliance_on_dr =~ q36_1 + q36_8
pharmacist_restriction =~ q36_6 + q36_7
side_effects =~ q36_4 + q36_5
'
cro.fit1 <- cfa(cro.model1, data=pers)
summary(cro.fit1, fit.measures = TRUE, standardized = TRUE)
 # standardizedSolution(rei.fit1)
 
cro.model2 <- '
# latent variable definitions
time pressures =~ q36_2 + q36_3
reliance_on_dr =~ q36_1 + q36_8
pharmacist_restriction =~ q36_6 + q36_7
'
cro.fit2 <- cfa(cro.model2, data=pers)
summary(cro.fit2, fit.measures = TRUE, standardized = TRUE)
 
select(pers, q36_2, q36_3) %>%
  omega(nfactors = 1) #.48

select(pers, q36_1, q36_8) %>%
  omega(nfactors = 1) #.41

select(pers, q36_6, q36_7) %>%
  omega(nfactors = 1) #.57
```


```{r}
ph.att <- select(pers, q37_1:q37_10)

vss(ph.att, fm = "mle")

fa.parallel(ph.att, fm = "ml")

ph.att.fit <- principal(ph.att, nfactors=2, rotate="oblimin")
ph.att.fit

ph.att.fit2 <- factanal(ph.att, 2, rotation="oblimin")
print(fit, digits=2, cutoff=.3, sort=TRUE)
```

